Participatory Mashups: Using Users to make Data Mashable

### 2008-09-29 papers/cscw_mash/cscw_mash.tex
Paper updates, largely guided by Beth suggestions

\author{
\alignauthor Rob Ennals\\
       \affaddr{Intel Research}\\
       \affaddr{2150 Shattuck Avenue}\\
       \affaddr{Penthouse Suite}\\
       \affaddr{Berkeley, CA 94704, USA}\\
       \email{robert.ennals@intel.com}
\alignauthor Beth Trushkowsky\\
       \affaddr{Computer Science Division}\\
       \affaddr{University of California at Berkeley}\\
       \email{trush@berkeley.edu}
}
\sloppy

@@

If we understand what the information on a page means then we can do useful things with it. We can connect the information to information elsewhere that might be relevant, we can compute new information from the information we have, and we can present users with new interfaces that are more useful than that provided by any individual site.

@@

Much of the most interesting information on the web is available as unstructured natural language text: arguments, ideas, opinions, factual claims, jokes. Much of this is information that could benefit a lot from being mashed up. For example ``which of these claims is likely to be wrong?'', ``what other sites disagree with this opinion?'', ``is there a more reliable source that backs up this claim?'', or ``what ideas on this site would I be likely to find most interesting?''. While natural language processing techniques have achieved a lot, understanding such information in a fully automated way is hard.

Similarly, there is a lot of structured information stored in the ``long tail'' of web sites that are too small for it to be worth a mashup author writing a custom scraper or API interface for, but which may nonetheless be very interesting. For example, tables of data that have been entered by hand, or one of the many tiny web sites that display data from a database backend using their own custom template that nobody has ever written a scraper for.

In this paper we argue for ``participatory mashups'' as a way to open up access to this data. In a participatory mashup we blur the line between the users and creators of a mashup by allowing the users of a mashup to teach the mashup how to understand new information, and how to connect information in new ways. By teaching a participatory mashup the meaning of some data, the user helps themselves, since the new information becomes part of the mashup they are interacting with, but they also help the wider community of users, since all other users can now benefit from the system understanding this data.

@@

More generally, we consider a tool to be a ``participatory mashup'' if it relies on users to teach it what information on the web means, and how that information is connected together. We argue that this is an approach that other applications could also use to help them understand the web.

@@

Much concern has been expressed recently about biased or inaccurate information on web sites~\cite{bbcwebwarning,wikifalse}, and the media echo chamber problem in which people read web sites that feed their own views back to them, rather than exposing them to the opposing opinions held by other groups~\cite{echochamber,echochamber2}.

Think Link~\cite{thinklink} is a Firefox extension that helps users evaluate the truth of statements they read, helps users be more easily exposed to a range of ideas and opinions that they might not otherwise encounter.

@@

Think Link maintains a graph of known factual claims, their relationship to each other, and the snippets that hold these claims (Figure~\ref{summarygraph}). This graph is built entirely by users of the tool. Users create claims, users connect claims, and users identify snippets making claims. Similarly, users vote for snippets, claims, or connections that they believe are particularly important.

@@

Our user study participants identified several reasons why they would want to mark up factual claims in documents they found. The most common reason people gave for identifying and organizing factual claims was if the person was writing an article or researching a topic and wanted to keep track of the information they had found. One user (who is an active blogger) also expressed an interest in finding and marking up instances of claims that he disagreed with, so that readers would see the arguments highlighted in red and be directed to the counter-arguments. The same user also expressed an interest in marking up claims in documents he had made in his own articles so that readers could quickly see the evidence he had found in support of his claims.

Like the work of Luis von Ahn~\cite{vonahn,recaptcha} or the ``invisible hand'' or Adam Smith the intention is that people should be motivated by self interest to do something that benefits the wider community.

@@

Mash Maker~\cite{mashmaker} is a browser extension that understands the meaning of the pages that users browse and suggests ways that it can improve the current page so as to be more useful to the user. Mash Maker relies on users to teach it both how to understand web pages, and also how particular kinds of web page might be improved in interesting ways.

As views a web page, Mash Maker will suggest ways that it can make the page more useful, and suggest these improvements on its tool bar. If the user clicks on the button for such an improvement then Mash Maker will apply it to the current page, potentially using other web sites and remote APIs, and potentially applying widgets that produce new visualizations or compute new data (Figure~\ref{mapinsert}). Mash Maker suggests improvements based on the meaning of the current page, the meaning of pages that the user has recently browsed, and the behavior of other users.

@@

Users can contribute to Mash Maker in several different ways. They can teach Mash Maker how to understand new kinds of web site, they can write new widgets, and they can show Mash Maker new ways that it can improve web pages that contain particular kinds of data. A user teaches Mash Maker how to extract information from a particular kind of web page by opening the Mash Maker extractor editor (Figure~\ref{extractedit}) and picking out examples of things on the page that the user thinks is interesting. As more users give Mash Maker more examples, Mash Maker gets better at understanding what pages mean. Unlike tools like Dapper~\cite{dapper} extractors are not owned by particular users. Instead an extractor is built up from examples given by all users on the web.

Given the huge number of differently formatted web sites on the web, it would not be practical for Mash Maker to be able to understand such a large range of web sites without users participating to teach in what different sites mean. For the users, the benefit of teaching Mash Maker how to understand a web site is that they get to use an enhanced version of the web site that Mash Maker has improved for them.

@@

Users teach Mash Maker ``patterns'' that Mash Maker can use to understand a large number of similarly formatted web pages (e.g. how to understand a flight listing on Expedia). This differs from Think Link, in which users pick out individual instances of factual claims which are not generalized to automatically find more snippets.

In the future, we plan to extend Think Link with natural language processing technology so that Think Link can automatically find new snippets, based on the examples it has been given. For example, if many users have shown Think Link example snippets that make the claim ``global warming is man made'', then Think Link could use these examples to find other snippets that may also be making this claim. At the simplest level, this could be done using simple textual similarity, similar to that done by Google Book Quotations~\cite{quotations}.

@@

The notion of a ``participatory mashup'' is somewhat fuzzy, and indeed some previous work can be considered to fit this description to some extent. To be a ``true'' participatory mashup, we believe a tool should not just allow users to contribute content, but allow users to teach it how to understand the meaning of content that already exists on the web, and use this knowledge to help other users of the tool.

reCAPTCHA~\cite{recaptcha} gives users the task of correctly transcribing scanned books as a test to see if they are human. Users thus unintentionally help machines better understand this information. Luis von Ahn has also shown how users can be persuaded to teach a system what data means by making it fun~\cite{vonahn}. Our approach to persuading users to teach us what data means is to make this data immediately useful to them.

>>>>

\author{
\alignauthor Rob Ennals\\
       \affaddr{Intel Research}\\
       \affaddr{2150 Shattuck Avenue}\\
       \affaddr{Penthouse Suite}\\
       \affaddr{Berkeley, CA 94704, USA}\\
       \email{robert.ennals@intel.com}
\alignauthor Beth Trushkowsky\\
       \affaddr{Computer Science Division}\\
       \affaddr{University of California at Berkeley}\\
       \email{trush@cs.berkeley.edu}
}
\sloppy

@@

If we understand what the information on a page means then we can do useful things with it. We can connect the information to information elsewhere that might be relevant, compute new information from the information we have, and present users with new interfaces that are more useful than that provided by any individual site.

@@

Much of the most interesting information on the web is in the form of unstructured natural language text: arguments, ideas, opinions, factual claims, jokes. Much of this is information that could benefit a lot from being mashed up. For example ``which of these factual claims is likely to be wrong?'', ``what other sites disagree with this opinion?'', ``is there a more reliable source that backs up this assertion?'', or ``what ideas on this site would I be likely to find most interesting?''. While natural language processing techniques have achieved a lot, understanding such information in a fully automated way is hard.

Similarly, there is a lot of structured information stored in the ``long tail'' of web sites that are too small for it to be worth a mashup author writing a custom scraper or API interface for, but which may nonetheless be interesting. For example, tables of data that have been entered by hand, or one of the many tiny web sites that display data from a database backend using their own custom template that nobody has ever written a scraper for.

In this paper we argue for ``participatory mashups'' as a way to open up access to this data. In a participatory mashup we blur the line between the users and creators of a mashup by allowing the users of a mashup to teach the mashup how to understand new information, and new connections between things. By teaching a participatory mashup the meaning of the data on a particular web page, the user helps themselves, since the mashup can now enhance that information for them, but they also help the wider community of users, since other users looking at the same page will be able to see an enhanced view, and the information on that page can now be used to enhance other pages on the web.

@@

More generally, we consider a tool to be a ``participatory mashup'' if it relies on users to teach it how to interpret and connect information on the web. We argue that this is an approach that other applications could also use to help them understand the web.

@@

Much concern has been expressed recently about biased or inaccurate information on web sites~\cite{bbcwebwarning,wikifalse}, and the media echo chamber problem in which people read web sites that feed their own views back to them, rather than exposing people to the opposing opinions held by other groups~\cite{echochamber,echochamber2}.

Think Link~\cite{thinklink} is a Firefox extension that helps users evaluate the truth of statements they read exposes users to a range of ideas and opinions that they might not otherwise encounter.

@@

Think Link maintains a graph of known factual claims, their relationship to each other, and the snippets that hold these claims (Figure~\ref{summarygraph}). This graph is built entirely by users of the tool. Users create claims, connect claims, and identify snippets making claims. Similarly, users vote for snippets, claims, or connections that they believe are particularly important.

@@

Our user study participants identified several reasons why they would want to identify and connect factual claims in documents they found. The most common reason was to organize information they had found while researching a topic or writing a document. One user (who is an active blogger) also expressed an interest in finding and marking up statements that he disagreed with, so that readers would see the arguments highlighted in red and be directed to the counter-arguments. The same user also expressed an interest in marking up claims made in his own articles so that readers could quickly see the evidence he had found in support of his claims.

@@

Mash Maker~\cite{mashmaker} is a browser extension that understands the meaning of the web pages that users browse and suggests ways that it can enhance the current page so as to be more useful to the user. Mash Maker relies on users to teach it both how to understand web pages, and also how particular kinds of web pages might be enhanced in interesting ways.

When a user views a web page, Mash Maker will suggest on its toolbar ways that it can enhance the web site to make it more useful. If the user clicks on the button for such an enhancement then Mash Maker will apply the enhancement to the current page, potentially using other web sites and remote APIs. An improvement can also use third-party widgets that produce new visualizations or compute new data (Figure~\ref{mapinsert}). Mash Maker suggests enhancement based on the meaning of the current page, the meaning of pages that the user has recently browsed, and the behavior of other users.

@@

Users can contribute to Mash Maker in several different ways. They can teach Mash Maker how to understand new kinds of web site, they can write new widgets, and they can show Mash Maker new ways that it can improve web pages that contain particular kinds of data. A user teaches Mash Maker how to extract information from a particular kind of web page by opening the Mash Maker extractor editor (Figure~\ref{extractedit}) and picking out examples of things on the page that the user thinks are interesting. As users give Mash Maker more examples, Mash Maker gets better at understanding what pages mean. Unlike tools like Dapper~\cite{dapper} extractors are not owned by particular users. Instead an extractor is built up from examples given by all users on the web.

Given the huge number of differently formatted web sites on the web, it would not be practical for Mash Maker to be able to understand such a large range of web sites without users providing some form of guidance. For the users, the benefit of teaching Mash Maker how to understand a web site is that they get to use an enhanced version of the web site that Mash Maker has improved for them.

@@

Users teach Mash Maker ``patterns'' that it can use to understand a large number of similarly formatted web pages (e.g. how to understand a flight listing on Expedia). This differs from Think Link, in which users pick out individual instances of factual claims which are not generalized to automatically find more snippets.

In the future, we plan to extend Think Link with natural language processing technology so that Think Link can automatically find new snippets, based on the examples it has been given. For example, if many users have shown Think Link example snippets that make the claim ``global warming is man made'', then Think Link could use these examples to find other snippets that may also be making this claim. At the simplest level, this could be done using textual similarity, similar to that done by Google Book Quotations~\cite{quotations}.

@@

The notion of a ``participatory mashup'' is somewhat fuzzy, and some existing systems fit this description to some extent. To be a ``true'' participatory mashup, we believe a tool should not just allow users to contribute content, but allow users to teach it how to understand the meaning of content that already exists on the web, and use this knowledge to help other users of the tool.

reCAPTCHA~\cite{recaptcha} gives a user the task of correctly transcribing text from a scanned book as a test to see if the user is human. Users thus unintentionally help machines better understand the books. Luis von Ahn has also shown how users can be persuaded to help a machine understand things by making the process fun~\cite{vonahn}. We persuade users to show us how to understand things by using the information to help the user themselves.
